Inducing Semantic Frames on a Very Large Corpus of Syntactic-Ngrams

### 2015-01-05 Paper/paperN.tex
Some copyedits and add an example.

\section{Introduction}
The growing number of digital publications contains too much information for a single human being to process, it is even hard to keep up to date on a particular topic. It would be usefull to be aided by technology that creates reliable summarizations. To ceate a summary is to extract the semantic content of a text and represent it in a human readable output. The first part of such a technology, extract semantic content, could also be an advantage for automatic stock trading systems. If it knows what is published about companies that is traded on the moment of publication it can make more profit.

Semantic content of a sentence can be represented in a frame. The main verbphrase of the sentence is the head of the frame and can be interpreted as predicate, representing the core of the episode described by the sentence, but the trick is to find out what the arguments of the predicate are. In linguistics argument selection is called case grammar \citep{dowty1991} and arguments (or roles) have specific names as \textit{agent - patient}. In computational systems names are not important and can be asigned when frame induction is complete.
The problem of semantic content can be illustrated by this simple example: \textit{'Alice buys a bread from the baker'} descibes the exact same situation as \textit{`The baker sells Alice a bread'}. Thus the semantic content of these sentences can be represented in one frame, where the head of the frame represents the core of the episode or situation and involvement is expressed by assigning roles to things or people. In general these roles can be anything like location, time, manner etc. For the sentences above the frame is depicted in \ref{framex}.
\begin{wraptable}{r}{.3\textwidth}
  \centering
 % \begin{table}
\begin{tabular}{|l l|}
  \hline
  \textit{\small predicate:\normalsize}&Transaction\\
  \hline
  \hline
  \textit{\small role 1:\normalsize} &baker\\
  \textit{\small role 2:\normalsize} &Alice\\
  \textit{\small role 3:\normalsize} &bread\\
  \hline
\end{tabular}
%\end{table}
\caption{Simple frame}
\label{framex}
\end{wraptable}
As the example above shows, the roles are represented by different syntactic parts of speech in both sentences, the object and subject are switched, furthermore, the verbs are different. But even with knowledge of specific vebrs which bear the same meaning with switched subject/indirect-object, we need to have technology to let machines generate semantic representations on top of syntacs in order to let machines be able to ( do as if they ) understand language and process new text in a meaningfull way. Hence, automatic semantic analysis and representation is required for further automatization.

The FrameNet project \citep{framenet} is an ongoing manual effort to define frames which could be mapped on a text to extract frames. But with the increasing amount of digital information, not to mention the inherent tediousness of building such a resource one word at a time, the prospect of (partially or completely) automating semantic frame induction is enticing. An automatic system could provide more complete descriptions of frames in current document banks and could better adapt to new words and evolving meanings.

In this project we investigate whether probabalistic latent-variable models can cluster verbs based on their meaning, which is inferred from the occurences of arguments it is encountered with. The clusters then make up a broader, but hopefully distinct, meaning. The data we use contains triples of verb-subject-object (see section \ref{data}), so induced frames contain only two roles. The models (described in section \ref{models}) induce frames based on the assumption the meaning of a verb relative to meaning of other verbs can be induced from its context. Hence the broader meaning is latent. To evaluate our models we use two metrics, one of which uses framenet data to check wheter the induced frames are similar to clusters of verbs in framenet, the other to check wheter the resulting frames are coherent, i.e. wheter the found clusters are not completely random. See section \ref{results} for more detail.

%\section{Related Work}
We based our work on two papers: \textit{`Inducing a semantically annotated lexicon via em-based clustering.'} by \citeauthor{rooth1999} and \textit{`Learning frames from text with an unsupervised latent variable model.'} by \citeauthor{oconnor2013}. In the first article clustering is realized by applying expectation maximalization on a simple model. This model produces frames in the form of 3 distributions, one for the predicate, a distribution over verbs, and two for the arguments, one distribution over subjects one over objects. A triple is assigned to a frame if the probability of this triple is highest in this frame. We will use this model as our baseline (as in the O'Connor paper). The second paper covers multliple models of which we implemented one. The difference with the baseline model is the assumption that a document uses a set of frames repeatedly as a rsult of a document having a (couple of) topics. [TODO: needs some further explanantion] In our data the tuples are not annotated with documents so we used this assumption in such a way that each verb covers one document.

>>>>

\section{Introduction}
The growing body of digital publications contains too much information for a single human being to process; it is even hard to keep up to date on a particular topic. It would be useful to be aided by technology that creates reliable summarizations. As a natural language processing task, summarization consists of two parts: first, extract the semantic content of a text, and then represent it in a condensed human readable output. The first part of such a technology, extracting semantic content, is what we deal with in this project. This step may also be useful on its own, for example, in automatic stock trading systems. Knowing what is published about publicly traded companies at the moment of publication can increase prophet margins for so-called high-frequnecy trading algorithms. Semantic representations have applications in other natural language procesing as well. For example, interlingua approaches to machine translation try to match sentences in the sorce and target language to a common generic semantic representation \cite{boas2005}.

Semantic content of a sentence can be represented in a frame. The main verbphrase of the sentence is the head of the frame and can be interpreted as predicate, representing the core of the episode described by the sentence. The trick is to find out what the arguments of the predicate are. In linguistics, argument selection is called case grammar \citep{dowty1991} and arguments (or roles) have specific names as \textit{agent - patient}. In computational systems names are not important and can be asigned when frame induction is complete.

The problem of semantic content can be illustrated by this simple example: \textit{'Alice buys a bread from the baker'} descibes the exact same situation as \textit{`The baker sells Alice a bread'}. Thus the semantic content of these sentences can be represented in one frame, where the head of the frame represents the core of the episode or situation and involvement is expressed by assigning roles to things or people. In general these roles can be anything like location, time, manner etc. The frame for the sentences above is depicted in table \ref{framex}.
\begin{wraptable}{r}{.3\textwidth}
  \centering
 % \begin{table}
\begin{tabular}{|l l|}
  \hline
  \textit{\small predicate:\normalsize}&Transaction\\
  \hline
  \hline
  \textit{\small role 1:\normalsize} &baker\\
  \textit{\small role 2:\normalsize} &Alice\\
  \textit{\small role 3:\normalsize} &bread\\
  \hline
\end{tabular}
%\end{table}
\caption{Simple frame}
\label{framex}
\end{wraptable}
As the example above shows, the roles are represented by different syntactic parts of speech in both sentences: the object and subject are switched. Furthermore, the verbs are different. Even given the knowledge of specific verbs that bear the same meaning with switched subject/indirect-object, we need to generate semantic representations on top of syntax in order to let machines (act as if they) understand language and process new text in a meaningfull way. Hence, automatic semantic analysis and representation is required for further automatization.

The FrameNet project \citep{framenet} is an ongoing manual effort to define frames which could be mapped onto text to give a semantic representation. But with the increasing amount of digital information, not to mention the inherent tediousness of building such a resource one word at a time, the prospect of (partially or completely) automating semantic frame induction is enticing. An automatic system could provide more complete descriptions of frames in current document banks and could better adapt to new words and evolving meanings.

In this project we investigate whether probabalistic latent-variable models can cluster verbs based on their meaning, which is inferred from the arguments with wich it occurs. These clusters then make up a broader, but hopefully distinct, meaning. The data we use contains triples of verb-subject-object (see section \ref{data}), so induced frames contain only two roles. The models (described in section \ref{models}) induce frames based on the assumption the meaning of a verb relative to meaning of other verbs can be induced from its context. Hence the broader meaning is latent. To evaluate our models we use two metrics, one of which uses framenet data to check wheter the induced frames are similar to clusters of verbs in framenet, the other to check wheter the resulting frames are coherent, i.e. wheter the found clusters are not completely random. See section \ref{results} for more detail.

%\section{Related Work}
We based our work on two papers: \textit{`Inducing a semantically annotated lexicon via em-based clustering.'} by \citeauthor{rooth1999} and \textit{`Learning frames from text with an unsupervised latent variable model.'} by \citeauthor{oconnor2013}. In the first article clustering is realized by applying expectation maximalization on a simple model. This model produces frames in the form of 3 distributions, one for the predicate, a distribution over verbs, and two for the arguments, one distribution over subjects one over objects. A triple is assigned to a frame if the probability of this triple is highest in this frame. We will use this model as our baseline (as in the O'Connor paper). The second paper covers multliple models of which we implemented one. The difference with the baseline model is the assumption that a document uses a set of frames repeatedly as a result of a document having a (couple of) topics. [TODO: needs some further explanantion] In our data the tuples are not annotated with documents so we used this assumption in such a way that each verb covers one document.
